---
title: "Hurricane"
author: "Chun Gao, Simu Huang"
date: "11/12/2020"
output: revealjs::revealjs_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(hurricaneexposuredata)
library(maps)
library(tmap)
library(sp)
library(sf)
library(viridis)
library(magrittr)
library(ggplot2)
library(ggpubr)
```

```{r}
## data from Fema, select data which incident type being "Hurricane" and happened between 2009 to 2018
df <- read.csv("PublicAssistanceFundedProjectsDetails.csv", header = TRUE)
df <- subset(df, df$incidentType == "Hurricane")
#summary(df$projectAmount)
#summary(df$federalShareObligated)
## delete data which is negative
df <- subset(df, df$projectAmount > 0 & df$federalShareObligated > 0)
df$year <- as.numeric(substr(df$declarationDate, 1,4))
df <- subset(df, df$year>=2009 & df$year <= 2018)
df <- df %>% mutate(ID=str_c(state,county,sep = ","))
df$ID <- tolower(df$ID)
dy <- df # store the data frame for yearly figure
```


```{r}
# unique(df$state)
counties_C <- c("alabama", "texas", "virgin islands of the U.S.", "north carolina", "massachusetts", "puerto rico", "new york", "virginia", "new hampshire", "maryland", "delaware", "west virginia", "louisiana", "florida", "new jersey", "vermont", "connecticut", "pennsylvania", "rhode island", "maine", "district of columbia", "mississippi", "ohio", "georgia", "south carolina", "american samoa", "hawaii") 
state_CB <- map_data("state", counties_C)
counties_CB<- map_data("county", counties_C)
```


# EDA
## the frequency distribution of disaster in terms of different years
```{r,warning=FALSE,message=FALSE}

du <- df
yearcount <- du %>% group_by(year) %>% summarize(count=sum(year!= "0"))
colors <- colorRampPalette(c("white","dark green"))(8)
ggplot(yearcount, mapping=aes(x=year, y=count)) +
  geom_bar(stat="identity",fill=colors)+
  labs(x="Year", y="Count") +
  theme_classic()
```

## the frequency distribution of damage in different states
```{r, warning=FALSE, message=FALSE}
ds <- df

statecount <- ds %>% group_by(state) %>% summarize(count=sum(state!= "0"))
statecount <- statecount[order(statecount$count), ]
# Georgia 2692
# Vermont	3218			
# North Carolina	6162			
# Texas	6914			
# Puerto Rico	7704			
# New Jersey	9576			
# Florida	10979			
# New York	13115	
## calculate the sum of frequency of rest of the states
topstate <- statecount[20:27,]
names(topstate) <- c("state","count")
restcount <- sum(statecount$count)-sum(topstate$count)
reststate <- data.frame("Rest States",restcount)
names(reststate)<-c("state","count")
newstate <- rbind(topstate, reststate)
newstate$percent_value = round(newstate$count/sum(newstate$count) * 100)
newstate$labs <- paste0(newstate$state, " (", newstate$percent_value, "%)")
ggdonutchart(newstate, "count",
			 label = "labs",
			 fill = "state",
			 lab.adjust = 0,
			 lab.font = c(4, "bold", "grey"),
			 color = "white",
			 palette = "Greens" ) + 
	coord_polar(theta = "y", start = 0, clip = "off")
```

## the distribution of damage category
```{r,warning=FALSE,message=FALSE}

dd <- df
damagecategorycount <- dd %>% group_by(damageCategory) %>%     summarize(count=sum(damageCategory!= "0"))
damagecategorycount <- damagecategorycount[order(damagecategorycount$count), ]
damagecategorycount$percent_value = round(damagecategorycount$count/sum(damagecategorycount$count) * 100)
damagecategorycount$labs <- paste0(damagecategorycount$damageCategory, " (", damagecategorycount$percent_value, "%)")
ggdonutchart(damagecategorycount, "count",
			 label = "labs",
			 fill = "damageCategory",
			 lab.adjust = 0,
			 lab.font = c(2, "bold", "grey"),
			 color = "white",
			 palette = "Blues" ) + 
	coord_polar(theta = "y", start = 0, clip = "off")

```



# Mapping

## Focus on "Project Amount"	
The estimated total cost of the Public Assistance grant project in dollars, without administrative costs. This amount is based on the damage survey.
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project from 2009 to 2018
df_c <- df %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
df_c <- df_c %>% 
  mutate(`Estimated Total Cost (USD)` = cut(df_c$projectAmount, 
                     breaks=c(0,100000,1000000,10000000,100000000,1000000000,10000000000,20000000000),
                     include.lowest = TRUE))
ttMap <- st_as_sf(maps::map("county",plot=FALSE,fill=TRUE))
df_c <- left_join(ttMap,df_c,by="ID")
df_c %<>% select(-projectAmount)
```

```{r}
# Mapping
tm_shape(df_c)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2009-2018',main.title.position="center")
```

## 2009
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2009
dy_2009 <- subset(dy, dy$year==2009)
dy_2009 <- dy_2009 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2009$projectAmount)
dy_2009 <- dy_2009 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2009$projectAmount, 
                     breaks=c(0,1000000,1500000,2000000,2500000,3000000,3500000),
                     include.lowest = TRUE))
tMap <- st_as_sf(map("county",counties_C ,plot=F,fill=T))
dy_2009 <- left_join(tMap,dy_2009,by="ID")
dy_2009 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2009)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2009',main.title.position="center")
```

## 2010
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2010
dy_2010 <- subset(dy, dy$year==2010)
dy_2010 <- dy_2010 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2010$projectAmount)
dy_2010 <- dy_2010 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2010$projectAmount, 
                     breaks=c(0,100000,500000,1000000,5000000,10000000,15000000),
                     include.lowest = TRUE))
dy_2010 <- left_join(tMap,dy_2010,by="ID")
dy_2010 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2010)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2010',main.title.position="center")
```

## 2011
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2011
dy_2011 <- subset(dy, dy$year==2011)
dy_2011 <- dy_2011 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2011$projectAmount)
dy_2011 <- dy_2011 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2011$projectAmount, 
                     breaks=c(0,500000,1000000,5000000,10000000,50000000,100000000,500000000),
                     include.lowest = TRUE))
dy_2011 <- left_join(tMap,dy_2011,by="ID")
dy_2011 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2011)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2011',main.title.position="center")
```

## 2012
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2012
dy_2012<- subset(dy, dy$year==2012)
dy_2012 <- dy_2012 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2012$projectAmount)
dy_2012 <- dy_2012 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2012$projectAmount, 
                     breaks=c(0,500000,1000000,5000000,10000000,50000000,100000000,500000000,1000000000,5000000000,10000000000),
                     include.lowest = TRUE))
dy_2012 <- left_join(tMap,dy_2012,by="ID")
dy_2012 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2012)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2012',main.title.position="center")
```

## 2013
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2013
dy_2013<- subset(dy, dy$year==2013)
dy_2013 <- dy_2013 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2013$projectAmount)
dy_2013 <- dy_2013 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2013$projectAmount, 
                     breaks=c(0,50000,100000,500000,1000000,5000000,10000000,50000000),
                     include.lowest = TRUE))
dy_2013 <- left_join(tMap,dy_2013,by="ID")
dy_2013 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2013)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2013',main.title.position="center")
```

## 2014,2015

Data missing for 2014 and 2015. 

## 2016
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2016
dy_2016<- subset(dy, dy$year==2016)
dy_2016 <- dy_2016 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2016$projectAmount)
dy_2016 <- dy_2016 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2016$projectAmount, 
                     breaks=c(0,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000),
                     include.lowest = TRUE))
dy_2016 <- left_join(tMap,dy_2016,by="ID")
dy_2016 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2016)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2016',main.title.position="center")
```

## 2017
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2017
dy_2017<- subset(dy, dy$year==2017)
dy_2017 <- dy_2017 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2017$projectAmount)
dy_2017 <- dy_2017 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2017$projectAmount, 
                     breaks=c(0,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000,1000000000,5000000000,10000000000,50000000000),
                     include.lowest = TRUE))
dy_2017 <- left_join(tMap,dy_2017,by="ID")
dy_2017 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2017)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2017',main.title.position="center")
```

## 2018
```{r,warning=FALSE,message=FALSE}
## the estimated total cost of Public Assistance grant project for 2018
dy_2018<- subset(dy, dy$year==2018)
dy_2018 <- dy_2018 %>% 
  group_by(ID) %>% 
  summarize(projectAmount = sum(projectAmount))
summary(dy_2018$projectAmount)
dy_2018 <- dy_2018 %>% 
  mutate(`Estimated Total Cost (USD)` = cut(dy_2018$projectAmount, 
                     breaks=c(0,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000,1000000000),
                     include.lowest = TRUE))
dy_2018 <- left_join(tMap,dy_2018,by="ID")
dy_2018 %<>% select(-projectAmount)
## Mapping
tm_shape(dy_2018)+
  tm_polygons("Estimated Total Cost (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Estimated Total Cost (USD)",
              palette = "Greens") + 
  tm_layout(main.title = 'Project_Amount 2018',main.title.position="center")
```


# Focus on "Federal Share Obligated"
The Public Assistance grant funding available to the grantee (State) in dollars, for sub-grantee's approved Project Worksheets.
```{r,warning=FALSE,message=FALSE}
df_d <- df %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
df_d <- df_d %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(df_d$federalShareObligated, 
                     breaks=c(0,100000,1000000,10000000,100000000,1000000000,10000000000,20000000000),
                     include.lowest = TRUE))
ttMap <- st_as_sf(map("county",plot=F,fill=T))
df_d <- left_join(ttMap,df_d,by="ID")
df_d %<>% select(-federalShareObligated)
```

```{r}
# Mapping
tm_shape(df_d)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2009-2018',main.title.position="center")
```

## 2009
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2009
dp_2009 <- subset(dy, dy$year==2009)
dp_2009 <- dp_2009 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2009$federalShareObligated)
dp_2009 <- dp_2009 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2009$federalShareObligated, 
                     breaks=c(0,500000,1000000,1500000,2000000,2500000),
                     include.lowest = TRUE))
tMap <- st_as_sf(map("county",counties_C ,plot=F,fill=T))
dp_2009 <- left_join(tMap,dp_2009,by="ID")
dp_2009 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2009)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2009',main.title.position="center")
```

## 2010
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2010
dp_2010 <- subset(dy, dy$year==2010)
dp_2010 <- dp_2010 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2010$federalShareObligated)
dp_2010 <- dp_2010 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2010$federalShareObligated, 
                     breaks=c(0,5000,10000,50000,100000,500000,1000000,5000000,10000000),
                     include.lowest = TRUE))
dp_2010 <- left_join(tMap,dp_2010,by="ID")
dp_2010 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2010)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2010',main.title.position="center")
```

## 2011
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2011
dp_2011 <- subset(dy, dy$year==2011)
dp_2011 <- dp_2011 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2011$federalShareObligated)
dp_2011 <- dp_2011 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2011$federalShareObligated, 
                     breaks=c(0,5000,10000,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000),
                     include.lowest = TRUE))
dp_2011 <- left_join(tMap,dp_2011,by="ID")
dp_2011 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2011)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2011',main.title.position="center")
```

## 2012
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2012
dp_2012 <- subset(dy, dy$year==2012)
dp_2012 <- dp_2012 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2012$federalShareObligated)
dp_2012 <- dp_2012 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2012$federalShareObligated, 
                     breaks=c(0,5000,10000,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000,1000000000,5000000000,10000000000),
                     include.lowest = TRUE))
dp_2012 <- left_join(tMap,dp_2012,by="ID")
dp_2012 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2012)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2012',main.title.position="center")
```

## 2013
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2013
dp_2013 <- subset(dy, dy$year==2013)
dp_2013 <- dp_2013 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2013$federalShareObligated)
dp_2013 <- dp_2013 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2013$federalShareObligated, 
                     breaks=c(0,5000,10000,50000,100000,500000,1000000,5000000,10000000,50000000),
                     include.lowest = TRUE))
dp_2013 <- left_join(tMap,dp_2013,by="ID")
dp_2013 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2013)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2013',main.title.position="center")
```

## 2014, 2015

Data missing for 2014 and 2015. 

## 2016
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2016
dp_2016 <- subset(dy, dy$year==2016)
dp_2016 <- dp_2016 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2016$federalShareObligated)
dp_2016 <- dp_2016 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2016$federalShareObligated, 
                     breaks=c(0,5000,10000,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000),
                     include.lowest = TRUE))
dp_2016 <- left_join(tMap,dp_2016,by="ID")
dp_2016 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2016)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2016',main.title.position="center")
```

## 2017
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2017
dp_2017 <- subset(dy, dy$year==2017)
dp_2017 <- dp_2017 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2017$federalShareObligated)
dp_2017 <- dp_2017 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2017$federalShareObligated, 
                     breaks=c(0,10000,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000,1000000000,10000000000,50000000000),
                     include.lowest = TRUE))
dp_2017 <- left_join(tMap,dp_2017,by="ID")
dp_2017 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2017)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2017',main.title.position="center")
```

## 2018
```{r,warning=FALSE,message=FALSE}
## the estimated Public Assistance grant funding available to the grantee (State) for 2018
dp_2018 <- subset(dy, dy$year==2018)
dp_2018 <- dp_2018 %>% 
  group_by(ID) %>% 
  summarize(federalShareObligated = sum(federalShareObligated))
summary(dp_2018$federalShareObligated)
dp_2018 <- dp_2018 %>% 
  mutate(`Public Assistance Grant Funding (USD)` = cut(dp_2018$federalShareObligated, 
                     breaks=c(0,10000,50000,100000,500000,1000000,5000000,10000000,50000000,100000000,500000000,1000000000),
                     include.lowest = TRUE))
dp_2018 <- left_join(tMap,dp_2018,by="ID")
dp_2018 %<>% select(-federalShareObligated)
## Mapping
tm_shape(dp_2018)+
  tm_polygons("Public Assistance Grant Funding (USD)",  border.col = "grey",
              lwd = 0.1, colorNA = NULL, style="cont",
              title = "Public Assistance Grant Funding (USD)",
              palette = "Blues") + 
  tm_layout(main.title = 'Federal_Share_Obligated 2018',main.title.position="center")
```

# Summary
<div style="font-size:18pt">



We can roughly see that in those 11 years, protective measures, public buildings, roads and Bridges suffered the most damage in the hurricanes.Between 2009 and 2019, New York suffered the most hurricanes, accounting for 17% of the country's total. The second is Florida and New jersey.

Meanwhile We can find that the cities that are hardest hit by hurricanes are those on the east coast, and they receive more aid each year.

</div>
